Automated Amortized Resource Bound Analysis \\ for Control Flow Graphs

### 2015-09-07 cfg/main.tex
some typos

A control flow graph (CFG) is a set a graph $G=(V,E,\labels)$ with
statement-labeled nodes. Here, $V$ is a set of nodes,
$E \subseteq V \times V$ is a set of edges, and
$\labels : V \to \statements$ is a mapping from nodes to statements.

@@

The derivation system for the automatic amortized analysis is defined
in~\pref{fig:auto}.  The derivation rules yield judgements of the form
$$
    \htriple{ \Gamma; Q }{ S }{ \Gamma'; Q' }.
$$
%
The judgement
can be seen as a quantitative Hoare triple.  All assertions are split into
two parts, the logical part and the quantitative part.  The
quantitative part $Q$ represents a potential function as a collection
of rational numbers $q_i$ indexed by the index set $I$.  The
logical part $\Gamma$ is left abstract but is enforced by our
derivation system to respect classic Hoare logic constraints.
%
The meaning of this basic judgment is as follows: If $S$ is executed
with starting state $\state$, the assertions in $\Gamma$
hold, $Q' {\ge} 0$, and at least $Q(\state)$ resources are available then the
evaluation does not run out of resources and, if the execution
terminates in state $\state'$, there are at least $Q'(\state')$
resources left and $\Gamma'$ holds for $\state'$.

@@

Let $G = (V,E,\labels)$ be a CFG. A potential annotation $\mathcal{P}$
for $G$ is mapping from notes $v \in V$ to pairs
$\left<(\Gamma,Q);(\Gamma',Q')\right>$ of quantitative assertions so
that the following holds.
%
\begin{enumerate}
\item  For every edge $(v_1,v_2) \in E$: 
  If $\mathcal{P}(v_1) = \left<(\Gamma_1,Q_1);(\Gamma'_1,Q'_1)\right>$ and 
   $\mathcal{P}(v_2) = \left<(\Gamma_2,Q_2);(\Gamma'_2,Q'_2)\right>$ then
   $\Gamma'_1 \models \Gamma_2$ and $Q_1' \geq Q_2$.
 \item For every node $v \in V$: If $\labels(v) = S$ and
   $\mathcal{P}(v) = \left<(\Gamma,Q);(\Gamma',Q')\right>$ then
  $\htriple{(\Gamma,Q)}{S}{(\Gamma',Q')}$.
\end{enumerate}

>>>>

A control flow graph (CFG) is a graph $G=(V,E,\labels)$ with
statement-labeled nodes. Here, $V$ is a set of nodes,
$E \subseteq V \times V$ is a set of edges, and
$\labels : V \to \statements$ is a mapping from nodes to statements.

@@

The derivation system for the automatic amortized analysis is defined
in~\pref{fig:auto}.  The derivation rules yield judgements of the form
$$
    \htriple{ \Gamma; Q }{ S }{ \Gamma'; Q' }.
$$
%
The judgement
can be seen as a quantitative Hoare triple.  All assertions are split into
two parts, the logical part and the quantitative part.  The
quantitative part $Q$ represents a potential function as a collection
of rational numbers $q_i$ indexed by the index set $I$.  The
logical part $\Gamma$ is left abstract but is enforced by our
derivation system to respect classic Hoare logic constraints.
%
The meaning of this basic judgment is as follows: If $S$ is executed
with starting state $\state$, the assertions in $\Gamma$
hold, and at least $Q(\state)$ resources are available then the
evaluation does not run out of resources and, if the execution
terminates in state $\state'$, there are at least $Q'(\state')$
resources left and $\Gamma'$ holds for $\state'$.

@@

Let $G = (V,E,\labels)$ be a CFG. A potential annotation $\mathcal{P}$
for $G$ is mapping from nodes $v \in V$ to pairs
$\left<(\Gamma,Q);(\Gamma',Q')\right>$ of quantitative assertions so
that the following holds.
%
\begin{enumerate}
\item  For every edge $(v_1,v_2) \in E$: 
  If $\mathcal{P}(v_1) = \left<(\Gamma_1,Q_1);(\Gamma'_1,Q'_1)\right>$ and 
   $\mathcal{P}(v_2) = \left<(\Gamma_2,Q_2);(\Gamma'_2,Q'_2)\right>$ then
   $\Gamma'_1 \models \Gamma_2$ and $Q_1' \geq Q_2$.
 \item For every node $v \in V$: If $\labels(v) = S$ and
   $\mathcal{P}(v) = \left<(\Gamma,Q);(\Gamma',Q')\right>$ then
  $\htriple{(\Gamma,Q)}{S}{(\Gamma',Q')}$.
\end{enumerate}
